What do incoming university students believe about open science practices in

### 2021-02-19 analysis/Manuscript.Rmd
finish the exclusion criteria section

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_pdf: default
  papaja::apa6_word: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  <!-- https://tinyurl.com/ybremelq -->
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: [Matt_Zotero_Library.bib,r-references.bib]
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

# participant numbers (all & included cases)
df_all <- df
n_all <- nrow(df_all)
df <- df_all %>% 
  filter(exclude %in% "include") # only those who met the inclusion criterion
n <- nrow(df)

@@

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]
  # exclude those who are younger than 18
  # only those who say "1" to eligibility are included; all other responses are excluded
  # those whose `status` variable is an 'IP Address' are included

age <- df_all %>%
  dplyr::count(age_lab)

el <- df_all %>%
  dplyr::count(eligibility_lab)

status <- df_all %>% 
  dplyr::count(status_lab)

@@

Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
participants who were not eligible to participate based on the combination of our
preregistered exclusion criteria. Specifically, we screened out people who were younger than 
18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
started a psychology unit at a university, regardless of whether they had 
completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
question (*n* = `r el[6,2]`). We also screened out an additional XX participants
who met our eligibility criteria, but did not respond to any of the main items
in the study.

@@

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

@@

<div id="refs" custom-style="Bibliography"></div>
\endgroup

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_pdf: default
  papaja::apa6_word: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  <!-- https://tinyurl.com/ybremelq -->
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Matt_Zotero_Library.bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

# participant numbers (all & included cases)
df_all <- df
n_all <- nrow(df_all)

# only participants who met the inclusion criterion
df <- df_all %>% 
  filter(exclude %in% "include") 
n <- nrow(df)

@@

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]
  # exclude those who are younger than 18 [7]
  # only those who say "1" to eligibility are included; all other responses are excluded
  # those whose `status` variable is an 'IP Address' are included

age_ex <- df_all %>%
  filter(age_criteria %in% "exclude") %>% 
  nrow()

el <- df_all %>%
  filter(eligibility_criteria %in% "exclude") %>% 
  dplyr::count(eligibility_lab) # need the breakdown by condition

status <- df_all %>% 
  filter(status_criteria %in% "exclude") %>% 
  dplyr::count(status_lab) # need the breakdown by condition

nmiss <- df_all %>% 
  filter(nmiss_criteria %in% "exclude") %>% 
  nrow()

@@

Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
participants who were not eligible to participate based on the combination of our
preregistered exclusion criteria. Specifically, we screened out people who were younger than 
18 years (*n* = `r age_ex`). We also screened out individuals who had already 
started a psychology unit at a university, regardless of whether they had 
completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
question (*n* = `r el[5,2]`). We then excluded additional responses that 
Qualtrics flagged as spam (*n* = `r status [1,2]`) or as a survey preview 
(*n* = `r status [2,2]`). Finally, we excluded participants who met all other 
eligibility criteria, but did not respond to any of the main items
in the study (*n* = `r nmiss`).

@@

## Data analysis
<!-- Can we move this to a reproducible code statement at the end? It works now -->

We used `r cite_r("r-references.bib")` for all our analyses.

@@

<div id="refs" custom-style="Bibliography"></div>

\endgroup
